Value-Suppressing Uncertainty Maps

### 2017-12-09 paper/main.tex
Outlining for new discussion section.

%\sizeFig

@@

The results from our initial evaluation of VSUPs are promising, showing that a general audience can make use of uncertainty information in a reasonable way. The way that uncertainty information is presented can have a measurable impact on decision-making. The VSUP strategy of only emphasizing differences when uncertainty is sufficiently low is somewhat analogous to the inferential statistics such as effects tests. VSUPs might therefore be used to promote more caution in judgments, and lead analysts away from spurious signals in data.

@@

Bivariate maps have an inherent limitation in that visual channels are often difficult to attend to separately or orthogonally. Bivariate maps are also complex to interpret. Systems which simultaneously display large amounts of value and uncertainty data to general audiences (such as Pangloss~\cite{moritz2017trust}) avoid them for precisely these reasons, relying instead on juxtaposed maps. Our results indicate that juxtaposition produces additional problems, forcing users that wish to integrate uncertainty and data to locate an item of interest, and then re-locate that same item in a visually distant map, which may have few visual landmarks in common. This additional step before information fusion is reflected in longer response times, and patterns of decision-making that are less mindful of risk.

>>>>

Our experimental results have a number of implications for designers wishing to employ bivariate maps for encoding uncertainty. Both of our experiments show that the way that uncertainty information is presented can have a measurable impact of decision-making. VSUPs make a number of design choices in presenting uncertainty. Firstly, they present uncertainty information simultaneously (superimposed) with value, rather than either of the other two strategies for comparing data in visualizations~\cite{gleicher2011visual}, juxtaposition or superposition. Secondly, they encode value and uncertainty in discrete, quantized bins, rather than continuously. Lastly, they alias and suppress uncertain, rather than certain, values. Our experiments provide specific performance information about the effects of each of these choices on information fusion tasks.

\subsection{Discrete vs Continuous Encodings}

\subsection{Juxtaposition vs. Superposition}

\subsection{Risk Aversion vs. Risk Seeking}
%\sizeFig

@@

%The results from our initial evaluation of VSUPs are promising, showing that a general audience can make use of uncertainty information in a reasonable way. The way that uncertainty information is presented can have a measurable impact on decision-making. The VSUP strategy of only emphasizing differences when uncertainty is sufficiently low is somewhat analogous to the inferential statistics such as effects tests. VSUPs might therefore be used to promote more caution in judgments, and lead analysts away from spurious signals in data.

@@

%Bivariate maps have an inherent limitation in that visual channels are often difficult to attend to separately or orthogonally. Bivariate maps are also complex to interpret. Systems which simultaneously display large amounts of value and uncertainty data to general audiences (such as Pangloss~\cite{moritz2017trust}) avoid them for precisely these reasons, relying instead on juxtaposed maps. Our results indicate that juxtaposition produces additional problems, forcing users that wish to integrate uncertainty and data to locate an item of interest, and then re-locate that same item in a visually distant map, which may have few visual landmarks in common. This additional step before information fusion is reflected in longer response times, and patterns of decision-making that are less mindful of risk.
